---
title: "MA678 Midterm project"
author: "Yuxi Wang"
date: "2020/11/29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(
'tidyverse'
)
```


## 1. Introduction
# In this project, Santander invites people to help them identify which customers will make a specific transaction in the future. The data provided for this competition has the same structure as the real data they have available to solve this problem. The data is anonymized.

# Loading the data
```{r}
train <- read.csv(file = "/Users/mac/Desktop/midterm/train.csv")

test <- read.csv(file = "/Users/mac/Desktop/midterm/test.csv")
```

## 2.Exploratory Data Analysis 

# 2.1 Data Summary

```{r}
head(train)
head(test)
```
After watching the first ten rows of two datasets, we can conclude:
1. As the project had presay, the names of every columns are anonymized, so we do not know what these variables' meaning.
2. There are many zero values present in the data.

```{r}
sum(is.na(train))
sum(is.na(test))
```
3. Neither the test set nor the training set has NAs.

However, since the data size is a little huge, we cannot easily use summary() or str() to have a simple understing of the data-set. So, I just count the rows and columns of training set and test set.
```{r}
print (paste("The number of records in training set:", dim(train)[1]))
print (paste("The number of features in training set:", dim(train)[2]))
print (paste("The number of records in test set:", dim(test)[1]))
print (paste("The number of features in test set:", dim(test)[2]))
```
As we can see, features in test set and training set are different. But this is because the tset set does not have target, and that is what I will do in test set if I take part in the competition. So, it does not metter. Also, test set is almost 10 times as that of training set. So, in order to easily running algorithms, I may mainly use training set to modeling.

# 2.2 Target variable
Since the purpose of training set is to let us use other predictors to fit the target variable. 
It is necessary to know as much information about the target variable as possible.

# 2.2.1 Let us first draw a scatter plot of the target variable.
As we can see, the dataset is very massive, so I have to rank the value to see the distribution plot of it.
```{r}
ggplot(train,aes(x=target,alpha=1/10,fill='red'))+
  geom_density()+
  guides(fill=FALSE,alpha=FALSE)
  
```

If we analysis the plot we can find that the distribution with majority of the data points having low value, and a huge amount of the data is 0. 
```{r}
ggplot(train,aes(x=log(target),y=..density..))+
  geom_histogram(fill='cornsilk',color='grey60',size=.2, alpha=.5)+
  geom_density()
  
```
So, now we know the desity of the target variable.


























